Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-29 paper_v1.tex
structured S1 results

\section{Study 1: Reasons for Disengaging}

@@

\subsubsection{Predictors}

RQ1: How do prior learner characteristics (demographics, geographic location, enrollment intentions, and previous online courses) influence learners' likelihood of disengaging from a MOOC?

@@

\subsubsection{Satisfaction}

RQ2a: What proportion of learners who disengaged were satisfied with their achievements in the course?

RQ2b: How does learners' behavior in the MOOC vary by their level of satisfaction?

@@

\subsubsection{Reasons}

RQ3a: What reasons do learners report for disengaging from a MOOC?

RQ3b: How do reasons for disengaging vary across prior learner characteristics (cf. RQ1)?

@@

We expected reasons for disengaging from the course to be related to the motivations that drove the learner to initially enroll in the course. A correlation matrix of learners' enrollment intentions and their subsequent reasons for disengaging revealed a small number of notable associations. Taking the course with friends or colleagues was correlated with disengaging because the course is not challenging enough, the material is too advanced of the learner's background, and the credential is not valuable enough to the learner ($r=.24, .20, .16$, respectively). Not surprisingly, learners who enrolled to experience an online course tended to stop participating because they were only exploring the course ($r=.17$). Learners looking to improve their English tended to experience technical difficulties ($r=.17$), and those who enrolled for personal growth and enrichment tended to struggle to keep up with deadlines ($r=.16$).

@@

\section{Conclusion}

>>>>

\section{Study 1: Understanding Attrition}

@@

\subsubsection{Predictors of Attrition}
% RQ1: How do prior learner characteristics (demographics, geographic location, enrollment intentions, and previous online courses) influence learners' likelihood of disengaging from a MOOC?

@@

\subsubsection{Satisfaction: Personal Success}
% RQ2a: What proportion of learners who disengaged were satisfied with their achievements in the course?
% RQ2b: How does learners' behavior in the MOOC vary by their level of satisfaction?

@@

\subsubsection{Reasons for Disengaging}
% RQ3a: What reasons do learners report for disengaging from a MOOC?
% RQ3b: How do reasons for disengaging vary across prior learner characteristics (cf. RQ1)?

@@

We expected reasons for disengaging from the course to vary by learner characteristics ($RQ3b$), such as learners' motivations for enrolling in the course. A correlation matrix of learners' enrollment intentions and their subsequent reasons for disengaging revealed a small number of notable associations. Taking the course with friends or colleagues was correlated with disengaging because the course is not challenging enough, the material is too advanced of the learner's background, and the credential is not valuable enough to the learner ($r=.24, .20, .16$, respectively). Not surprisingly, learners who enrolled to experience an online course tended to stop participating because they were only exploring the course ($r=.17$). Learners looking to improve their English tended to experience technical difficulties ($r=.17$), and those who enrolled for personal growth and enrichment tended to struggle to keep up with deadlines ($r=.16$).

@@
